---
title: "Rendering HTML outputs"
output: html_notebook
---

This notebook renders HTML outputs from the 01 notebook through *parameterisation*.

First we import the data in order to generate a list of forces that we can use to specify the parameters and name the files.

```{r import data}
#store the url of one sheet in the google doc
forceanalysisurl <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQl7Qa0qk4BGjFH9puBAN4aheTDKV1dBhcAGQXSFLSpukDaEQDEmijGMOxXcjw9F-gUfUSSjVoLVUQs/pub?gid=1174732273&single=true&output=csv"
#while testing we use this fake data
#fakedataurl <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSMLZJaBx-BknWGEvitVulHDmJWTFUrko7nOuUWpRRBp3cBV6-67o6-iI9Oyc9CVSEpuDNtQ49M0EJM/pub?gid=1434769906&single=true&output=csv"
#forceanalysisurl <- fakedataurl
#fetch the data at that url
grabtheforces <- read.csv(forceanalysisurl, stringsAsFactors = F)
#remove the last 'grand total' row
grabtheforces <- grabtheforces[-40,]
#just get one column - it's now a vector
force <- grabtheforces$Force
#remove BTP (3rd force) as it causes an error and we don't need it anyway
force <- force[-3]
```

The code below takes the Rmd file named and renders a .md file for each force (even though the file itself specifies html_document as its output). This is because the next notebook then renders the entire folder as a website, so the HTML in those .md files becomes active.

```{r generate html files}
#store the location of the paramsfile to use below
paramsfile <- "01forcetemplateMDversion.Rmd"
#loop through all regions - but this just creates the same file and overwrites it each time, ending with the last item (Yorkshire)
for (r in force) {
  rmarkdown::render(paramsfile, params = list(force = r), output_file = paste(sep="",'site/',r,'.md'),
    envir = parent.frame())
}
#more at https://bookdown.org/yihui/rmarkdown-cookbook/rmarkdown-render.html
```

