---
title: "Render and clean"
output: md_notebook
---

# Rendering the website and cleaning the HTML files

* In notebook 1 a template was created that could be used to generate text descriptions and tables for each force
* In notebook 2 dozens of different webpages were generated from that template

This notebook details the next step: combining those pages into a website, and generating an index page.

## Store a list of markdown files

First, we need to store a list of all the files that are going to be used. These are in a folder called 'site'.

We then loop through those file names and, for those which end in '.md', we use those names to generate some code and store it in a YAML file.

```{r get file names and generate yaml}
#get the names of all the html files
filenames <- list.files("site")

#store the string we want to start out yaml file with
yamlstring <- 'name: "iopc"
navbar:
  title: "Police misconduct"
  left:
    - text: "Forces"
      menu:'

#create an empty vector to store all the strings we're about to create
strvec <- c()

#loop through the filenames 
for (i in filenames){
  if(substring(i,nchar(i)-2,nchar(i)) == ".md" ){
    #replace spaces with dashes, and replace the file extension with .html
    htmlversion <- gsub(" ","-",gsub(".md",".html",i))
    #get the name by removing the file extension. Also remove 'Police'
    textversion <- gsub(" Police| Constabulary","",gsub(".md","",i))
    #create a string for the YAML file by inserting those
    fullstring <- paste0('
      - text: "',textversion,'"
        href: ',htmlversion)
    strvec <- c(strvec,fullstring) #add to the collection of strings 
  }
}

#add the initial string
strvec <- c(yamlstring, strvec)

#create a yaml file with that string of text in it
write(strvec, file = "site/_site.yml")
```

## Render the files

Finally, we use the `render_site` function to specify the folder containing all the files for the site. The YAML file will be used to generate a menu, among other things.

```{r render site}
#now render the site
rmarkdown::render_site("site")
```

We also want to render the index file. 

## Clean the HTML outputs

The force pages have some HTML which needs to be removed because it is being rendered as paragraph text: `<p>&lt;!DOCTYPE html&gt;</p>`.

```{r list html files}
#get the names of all the html files
htmlfiles <- list.files("site/_site")
#read in the first one
testfile <- read_lines(paste0("site/_site/",htmlfiles[1]))
#show the 170th line
testfile[170]
#replace it
testfile[170] <- ""
testfile[170]
#save it as a HTML file to check
write(x = testfile, file=paste0("site/_site/","testfile.html"))
#remove the variable
rm(testfile)
```

Once tested, we embed that process in a loop which tests if the file is one of the force pages (all of which end in 'Police.html' or 'Constabulary.html') and then removes the offending line if so.

```{r clean all files}
#loop through the list of filenames
for (i in htmlfiles){
  print(i)
  #extract the last 5 chars
  filetype <- substring(i,nchar(i)-5,nchar(i))
  #check if they end in e.html or y.html
  ey <- filetype == "e.html"|filetype == "y.html"
  print(filetype)
  #this should be TRUE or FALSE
  print(ey)
  #if it's a police/constabulary html file
  if(ey){
    #read in that file
    thisfile <- read_lines(paste0("site/_site/",i))
    #show first line
    print(thisfile[170])
    #if it has that text
    if (thisfile[170] == "<p>&lt;!DOCTYPE html&gt;</p>"){
      print("OH!")
      #replace specified string
      thisfile[170] <- ""
      write(x = thisfile, file=paste0("site/_site/",i))
    }
    else {
      print("NOPE")
    }
  }
  else {
    print("NOT THIS ONE")
  }
}
```

### Clean up the index page menus

We also need to clean the dropdown menu in the index page: by default this lists all the forces but is too long to fit on one screen and cannot be scrolled. 

So we need to split it into two menus instead.

```{r clean index menu}
#the index file should be the 20th in the previous list
htmlfiles[20]
#read it in
indexfile <- readr::read_lines("site/_site/index.html")
#line 257 should be the title of the dropdown, 'Forces'
indexfile[257]
#change it
indexfile[257] <- "Forces A-M"
indexfile[257]
#line 325 should be the beginning of the first N force, Norfolk
indexfile[325:326]
#add HTML which closes the first part of the list and begins a second list with a dropdown button
#code taken from https://github.com/sduiopc/test1/blob/8938ef49cf45eb5cb67ab73974c8bdbf33aee4c5/index.html
#which is the version where I did this manually
indexfile[325] <- '</ul></li></ul><ul class="nav navbar-nav navbar-right"></ul><ul class="nav navbar-nav"><li class="dropdown"><a href="#" class="dropdown-toggle" data-toggle="dropdown" role="button" aria-expanded="false">Forces N-Z<span class="caret"></span></a><ul class="dropdown-menu" role="menu"><li>'
indexfile[325:326]
#save file
write(x = indexfile, file=paste0("site/_site/","index.html"))
#remove the variable
rm(indexfile)
```

